\documentclass[letterpaper,10pt,draft]{amsart}
% \usepackage[utf8]{inputenc}         % or whatever you use
% \usepackage[T2A,T1]{fontenc}
% \usepackage[square,sort,comma,numbers]{natbib}


% % % 
% % % Flag that everything is compiled for thesis itself 
% % % 
\def \projectcompilation {test}

\input{proj.hyphenation}
\input{proj.headercore}
\input{proj.mathletterstyles}


\begin{document}

\title
[Bases FEEC]
{Construction of Matrices in FEEC}

\author{Martin W. Licht}

\address{UCSD Department of Mathematics, 9500 Gilman Drive MC0112, La Jolla, CA 92093-0112, USA}

\email{mlicht@math.ucsd.edu}

\thanks{
This research was supported in part by NSF DMS/RTG Award 1345013 and DMS/CM Award 1262982.
Parts of this article are based on the author's PhD Thesis.}

\subjclass[2010]{65N30}

\keywords{barycentric differential form, canonical spanning sets, degrees of freedom, finite element exterior calculus, geometrically decomposed bases}


\begin{abstract}
 THis informal document describes the construction of finite element matrices 
 in the contex to finite element exterior calculus.
 We consider the mass matrix, derivative and trace matrices,
 and some auxiliary constructions.
 % 
\end{abstract}

\maketitle 

\section{Introduction} \label{sec:introduction}

In this paper we discuss a finite element code 
based on finite element exterior calculus. 
The main point is to illustrate how the mathematical concepts of FEEC 
allow the easy implementation of Lagrange elements, curl-conforming elements, and divergence-conforming elements 
for any polynomial order and any dimension. 

Finite-Elemente-Methoden sind ein bekanntens Verfahren zur numerischen Lösung partieller Differentialgleichungen.
Vektoranalysis ... 
FEEC .... 

A major advantage of FEEC is that it describes finite element spaces 
of arbitrary polynomial degree and dimension 
in a unified framework. 

\section{Notation and Preleminaries}

A $d$-dimensional simplex is the convex closure of $d+1$ affinely independent points,
which are called the vertices of the simplex. 
A simplex $S$ is a subsimplex of another simplex $T$ 
if the vertices of $S$ are a subset of the vertices of $T$.

\section{Local Operations}

We let $\hat T$ denote the reference simplex. 

We recall the formula 
\begin{align*}
 \int_{T} \lambda^{\alpha} \dif x = ....
\end{align*}

\begin{align*}
 \omega
 = 
 \sum_{i} \omega_{i} \cartanlambda^{T}_{i}
 = 
 D\Phi^{-T} \sum_{i} \omega_{i} \cartanlambda^{\Delta}_{i}
 .
\end{align*}
\begin{align*}
 e_{j} \cdot \omega
 = 
 e_{j} \cdot D\Phi^{-T} \sum_{i} \omega_{i} \cartanlambda^{\Delta}_{i}
 = 
 D\Phi^{-1} e_{j} \cdot \sum_{i} \omega_{i} \cartanlambda^{\Delta}_{i}
 = 
 \sum_{i} \omega_{i} D\Phi^{-1} e_{j} \cdot \cartanlambda^{\Delta}_{i}
 .
\end{align*}
This means that $e_{j} \cdot \omega$ is the inner product of the coefficient vector 
$(\omega_{i})_{i}$ with the $j$-th column of $D\phi^{-1}$.
The latter vector is the $j$-th row of $D\Phi^{-T}$.
So the standard basis coefficients of $\omega$ are given by 
the matrix-vector product $D\Phi^{-T} \cdot (\omega)$.
Conversely, the coefficients in the barycentric basis 
are obtained by multiplying the coefficient vector of the unit basis 
by matrix $D\Phi^{T}$.

\section{Piecewise Algebraic Operations}

\section{Piecewise Mass Operation}

\section{Interpolation of Fields}


\section{Global to Local Matrix}

Whitney forms are associated to subsimplices of the triangulation. 
Furthermore, boundary conditions are imposed by filtering out certain subsimplices.
We define the matrix which maps the continuous space of Whitney forms
to the broken space of piecewise Whitney forms.



\section{Shape Functions}

We associate a space of shape functions with every simplex $S$,
which are either extensions of the space $\mathring\calP_{r}\Lambda^{k}(S)$
or $\mathring\calP_{r}^{-}\Lambda^{k}(S)$.

\footnote{We use the term \textit{function} not only for scalar-valued functions
but also vector- and tensor-valued functions.}




  \bibliographystyle{siam}
  \bibliography{library}

  
\end{document}
